### 2021-11-25 input/proposal.tex
reworking proof of detection

  \noindent Assuming a chain of delivery $C = [x, \ldots, z]$ of
  $\alpha_x$ with $\alpha_x = \min D_z$, and assuming $d_x(\delta_x)$,
  then by (A), the staleness notification reaches a \process $y\in C$

  every \process eventually deliver and forward $\delta_x$ either
  following the same chain, except if $\alpha_x$ is already stale
  which

  $z$ does not receive, hence deliver $\delta_x$ when a \process $y$
  between $x$ and $z$ stops forwarding $\delta_x$ because it delivered
  another message $\alpha_s$ with $\alpha_s < \alpha_x$.

  Assuming a chain of \processes $[x, x_2, \ldots, y]$ such that
  $\alpha_x \min D$

  Assuming $[x, x_2, \ldots, x_k, y, y_1, y_2, \ldots, y_\ell, z]$,

  (i) If every \process (such as $a$) starting from the source
  delivers and forwards a removal notification $\delta_X$ when their
  last delivery is $\alpha_X$, then every such \process eventually
  delivers the removal notification $\delta_X$ except \processes (such
  as $b$) that delivered $\alpha_X$ from a \process that delivered a
  message from another partition $\alpha_Y$ since then.

  These exceptions eventually receive and deliver $\alpha_Y$ since
  $\alpha_Y$ is better than $\alpha_X$ through this path, except if
  they already received and delivered the removal notification of
  $P_Y$ (such as $c$). These \processes may never receive hence
  deliver $\delta_X$, and may never receive hence deliver a better
  message than $\alpha_X$. They need an additional mechanism to
  eventually purge $\alpha_X$ that cannot rely on the eventual purging
  of $P_Y$ at \processes like $b$, to avoid deadlocks.

  (ii) Assuming that every \process keeps an history of its past
  deliveries, \processes (such as $c$) can detect the inconsistency,
  since they receive from their parent an already deleted partition
  $P_Y$. This notification means that the parent discards any
  $\delta_Z$ with $\alpha_Z^z < \alpha_Y^y$, and most importantly, if
  $\delta_X$ exists, it discards it. To ensure the purge of stale
  messages, a detecting \process must assume the worst case that such
  $\delta_X$ exists, and send another kind of message, noted $\Delta$,
  that notify the possible removal of $P_X$.

  (iii) A \process (such as $d$) whose last delivery is $\alpha_X$,
  but whose parent is neither inconsistent (like $b$) nor receiving
  $\delta_X$ (like $a$), eventually receives $\Delta$ from a detecting
  \process, either directly or transitively, for such a child \process
  ($d$) trusts the possible removal of $P_X$ by delivering and
  forwarding such $\Delta$. $\Delta$ suffers from identical blocking
  conditions (between $b$ and $c$) than $\delta$, leading to the same
  solutions of detection and propagation of $\Delta$. Eventually,
  every \process whose last delivery is $\alpha_X$ receives and
  delivers either a better $\alpha_Z$, or $\delta_X$, or $\Delta_X$.
\end{proof}

>>>>

  \noindent (B) Assuming a chain of delivery $C = [x, \ldots, z]$ of
  $\alpha_x$ with at least $\alpha_x = \min D_z$, and assuming
  $d_x(\delta_x)$, then by (A), the staleness notification reaches a
  \process $C[k]$. By Definition~\ref{def:fs}, the fowarding stops
  when $C[k]$ already delivered $\delta_x$ (covered by (A)) or
  delivered a better message $\alpha_x \neq \alpha_y = \min
  D_{C[k]}$. The latter means that $\eventually d_{C[k+1]}(\alpha_y)$
  or $\delta_y \in D_{C[k+1]}$.

  %% (iii) A \process (such as $d$) whose last delivery is $\alpha_X$,
  %% but whose parent is neither inconsistent (like $b$) nor receiving
  %% $\delta_X$ (like $a$), eventually receives $\Delta$ from a detecting
  %% \process, either directly or transitively, for such a child \process
  %% ($d$) trusts the possible removal of $P_X$ by delivering and
  %% forwarding such $\Delta$. $\Delta$ suffers from identical blocking
  %% conditions (between $b$ and $c$) than $\delta$, leading to the same
  %% solutions of detection and propagation of $\Delta$. Eventually,
  %% every \process whose last delivery is $\alpha_X$ receives and
  %% delivers either a better $\alpha_Z$, or $\delta_X$, or $\Delta_X$.
\end{proof}
